Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-11 doc_v2/doc_v2.Rmd
rescaled image

\begin{figure}
\centering
\includegraphics[width=\textwidth]{images/B6-B2-L6.png}
```{r, echo=FALSE, fig.width=8, fig.height=3, out.width='\\textwidth'}
land <- read.csv("../data/b6b2l6.csv")
land %>% ggplot(aes(x = y, y=resid)) +geom_line() +theme_bw()
```

\caption{\label{fig:rgl} Image of a bullet land from a confocal light microscope at 20 fold magnification.}

>>>>

\hh{figure \ref{fig:rgl} needs to be mentioned somewhere in the write-up}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{images/B6-B2-L6-rescaled.png}
```{r, eval=FALSE, echo=FALSE, fig.width=8, fig.height=3, out.width='\\textwidth'}
land <- read.csv("../data/b6b2l6.csv")
land %>% ggplot(aes(x = y, y=resid)) +geom_line() +theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep="")))
```

\caption{\label{fig:rgl} Image of a bullet land from a confocal light microscope at 20 fold magnification (top) and a chart of the corresponding signature of the same land (bottom). The dotted lines connect some peaks visible in both visualizations.}
